CRUSE to Safe Cycling in Ireland

### 2023-09-26 paper.qmd
eval=FALSE
Add docx

# Uncomment for draft versions:
format: 
  html: default
#   # docx: default
#   # pdf: default

@@

```{r}
#| include: false
library(tidyverse)
remotes::install_dev("tmap")
library(tmap)
```

>>>>

# Uncomment for draft versions:
format: 
  html: default
  docx: default
#   # pdf: default

@@

```{r}
#| include: false
#| eval: false
library(tidyverse)
remotes::install_dev("tmap")
library(tmap)
```
